Blocking-resistant communication\\through domain fronting

### 2014-07-29 docs/meek.tex
Use new flowduration graph.

\subsection{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google did a user make 
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1 ~ 10. This is not unexpected
because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:duration:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek (Notice the x-axis)}
\label{fig:duration:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:duration}
\end{figure*}

\subsection{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure ~\ref{fig:duration:lbl} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure ~\ref{fig:duration:meek}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.

>>>>

\subsection{Concurrent connections}
Figure ~\ref{fig:connections} shows how many HTTPS connections to Google user made
during the 10-minute measurement window.
There are 34,732 connections in total from 2,745 unique IPs. We observe that the majority of users have less than 
50 connections to the Google frontend server, and most of the numbers concentrate on 1--10.

% David: I think this needs to be justified. Leaving Gmail open all day is a common use case,
% as is YouTube, as is finding +1 buttons and Google-source JavaScript on unrelated web sites.
% This is not unexpected
% because a typical pattern of using Google is using the Google search as a stepping stone for other websites.

@@

\begin{figure}
\centering
\includegraphics[width=\linewidth]{flowduration}
\caption{CDF of connection lifetime.}
\label{fig:duration}
\end{figure}

\subsection{Connection lifetime}
We consider the connection lifetime as a potential weakness. Figure~\ref{fig:duration} shows the 
connection lifetime distribution of normal traffic. Interestingly we can see the concentration on 
several discrete values: 60s, 120s, 180s, 240s. We hypothesize that it is due to the HTTP Keep-Alive 
timeout of different browsers and web services. Another important observation is the concentration on 
durations that exceed 600 seconds. Note that our trace only contains 10 minutes' data, therefore the concentration 
on 600 seconds does not reflect that these connections' actual duration is 600 seconds. Rather, 600 seconds
is the lower bound of their actual duration. Thus, we can conclude that only about 10\% connections last 
longer than 600 seconds.

The distribution of meek's traffic, in contrast, is totally different. First, there are much fewer connections, which is 
consistent with the discussions above. Second, the durations are much longer if we notice the x-axis in Figure~\ref{fig:duration}. If there is not a case in which normal users also have such long connections when browsing Google, the 
censor can potentially block any long connections between users and Google. Even if this is the case, the
censor has to wait until a time threshold is reached. The user might have already obtained the forbidden data she wants, or 
meek could simply restart a connection.
